Enhancing the prediction of sales for newly published books by means of computational intelligence methods

### 2016-05-04 paper.tex
Replacing 'publishing house/s' for 'company/ies' to unify the text and also because the names used for the examples look cooler with the 'Co'

With this issue in mind, in this paper we firstly present an analysis on the aforementioned real dataset, by means of data mining and visualisation techniques. Then, a feature selection process is conducted using three different methods, in order to find out what are the relevant variables describing a book in the prediction (or regression) procedure. After this, a forecasting stage is performed applying a set of regression algorithms to the different datasets (considering a different number of variables).
The value of this methodology is contrasted considering four different publishing houses being representative as top sellers, medium sellers, the most varied and one which sells a medium amount of different books.

The rest of this paper is structured as follows: next, Section \ref{sec:soa} presents a comprehensive review of the approaches found in the bibliography related to the prediction of sales in similar scopes. 
Then, Section \ref{sec:problem} introduces the problem of the estimation of print-run for new books, along with a description of the considered dataset.
Section \ref{sec:methodology} details the methodology considered in the study, from the data collection and preprocessing stages, to the selection of the forecasting methods to be applied in the experiments.  These are reported in Section \ref{sec:experiments}, which is also devoted to analyse the obtained results in feature selection and book sales forecasting using different datasets (with different amounts of features) for all the publishing houses. The results obtained for the four considered special cases are commented in Section \ref{sec:example_cases}. Finally, conclusions and future lines of work are presented in Section \ref{sec:conclusionsAndFutureWork}.

@@

First, after the publishing house has provided the raw data
(extracted directly from its database), a preprocessing method has
% This should go to the previous section. 
been performed in order to remove incorrect or incoherent patterns,
such as those with null values in required variables, or with negative
sales, for instance. Moreover, the initial set of variables (presented
in Table \ref{tabla:paramsOrig50}) has been reduced by an expert to
use just those that can be known in advance when a new book is
launched, i.e. \textit{pre-sales data}.

@@

Once the models and results have been obtained for the whole dataset, the same methodology has been applied to some specific cases (publishing houses) in order to prove the value of the proposal.
Some specific interpretable models have been created as a final result of the work. The aim is that these will cold be used as a decision-aid tool for the experts who have to take decide about the best print-run quantity for new published books, in order to, logically maximise the benefit (or minimise the costs).

@@

Regarding the feature \textit{publisher}, we have removed it from the final dataset since it is indeed included in the code of \texttt{collection}. In addition, we think it is not really relevant for the accuracy of the models and, moreover, publishers will not consider the results in other publishing houses for predicting its own sales.
% Antonio - Think about this... should we mention this?

@@

We have analysed the whole dataset (all the publishing houses), but also performed some experiments considering specific publishing houses as example cases.
The obtained decision trees have been plotted to show their simplicity and their real value as a decision-aid tool for publishers.

@@

\section{Experiments of special publishing houses cases}
\label{sec:example_cases}

This section presents further experiments conducted on data concerning four interesting special publishing house cases. These publishing houses were selected as representative cases which could be very interesting for decision makers and managers in the domain. The four cases are described as follows:

\begin{itemize}
    \item Best seller publishing house: this case represents the publishing house that sells the highest number of copies regardless the title of the books sold. Therefore, it is an example of a case on a higher business scale.
    \item Medium seller publishing house: this represents an publishing house that sells medium number of copies compared to the other publishing houses (Medium business scale). 
    \item Highest variation publishing house: this is an example of an publishing house that follows a strategy in publishing a very wide range of different titles.
    \item Medium varied publishing house: this case represents an publishing house that has a median rank between the other publishing house regarding the variety of titles sold.
\end{itemize}

Table \ref{Table:special_cases} shows number of sold copies and number of titles published by the selected publishing houses.

\begin{table}
\caption{Description of publishing houses considered as special cases.
\label{tab:desc_publishing houses}}
\centering{}%
\begin{tabular}{|c|l|l|l|}
\hline 
 Case & Different books sold & Total copies sold & Description\\
\hline 
\textit{All publishing houses} & 6083 & 3201645 & 209 publishing houses\\
\hline 
\textit{UDL929} & 216 & 460752 & Best selling publishing house\\
\hline 
\textit{UDLW12} & 97 & 2635 & Medium selling publishing house\\
\hline 
\textit{UDL704} & 293 & 58236 & Publishing house with most different\\ 
       &     &       & books sold\\
\hline 
\textit{UDLU11} & 180 & 249481 & Publishing house with medium number\\ 
       &     &       &  of different books sold\\
\hline 
\end{tabular}
\label{Table:special_cases}
\end{table}

@@

\begin{table}
\caption{Predicting Total sales for Publishing house-UDL929 (The best selling publishing house) }
\centering{}%
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
 & $R^{2}$  & MAE  & RMSE  & RAE (\%)  & RRSE (\%)  & Time (s)\tabularnewline
\hline 
\hline 
M5P  & 90.0 $\pm$0.10 & 670.24 $\pm$181.05  & 1065.34 $\pm$413.84  & 40.83 $\pm$10.86  & 43.56 $\pm$19.87  & 0.03 $\pm$0.002\tabularnewline
\hline 
K-NN  & 73.3 $\pm$0.19  & 1057.21 $\pm$385.04  & 1875.85 $\pm$916.96  & 61.88 $\pm$12.37  & 68.75 $\pm$15.98  & 0 $\pm$0.0001\tabularnewline
\hline 
RF  & 87.6 $\pm$0.11  & 771.83 $\pm$326.34  & 1490.49 $\pm$930.58  & 45.40 $\pm$14.14  & 55.91 $\pm$31.70  & 0.08 $\pm$0.004\tabularnewline
\hline 
LR  & 86.3 $\pm$0.12  & 922.33 $\pm$289.01  & 1399.84 $\pm$619.62  & 56.11 $\pm$16.17  & 56.43 $\pm$25.09  & 0.005 $\pm$0.001\tabularnewline
\hline 
SVM  & 86.7 $\pm$0.1  & 873.22 $\pm$345.16 & 1621.48 $\pm$985.24  & 50.85 $\pm$11.83  & 57.23 $\pm$20.40  & 0.04 $\pm$0.016\tabularnewline
\hline 
\end{tabular}
\label{Table:case1results}
\end{table}

\begin{table}
\caption{Predicting Total sales for PublishingHouse-UDLW12 (The median selling publishing house) }
\centering{}%
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
 & $R^{2}$  & MAE  & RMSE  & RAE (\%)  & RRSE (\%)  & Time (s)\tabularnewline
\hline 
\hline 
M5P  & 83.2 $\pm$0.24  & 14.18 $\pm$6.62  & 23.82 $\pm$11.86  & 43.41 $\pm$20.39  & 55.79 $\pm$30.47  & 0.009 $\pm$0.002\tabularnewline
\hline 
K-NN  & 79.3 $\pm$0.24 & 15.34 $\pm$8.71  & 26.57 $\pm$16.64  & 46.20 $\pm$23.77  & 60.09 $\pm$35.21  & 0.0001 $\pm$0.0002\tabularnewline
\hline 
RF & 85.8 $\pm$0.17  & 14.19 $\pm$6.69  & 23.57 $\pm$11.83  & 42.53 $\pm$16.80  & 53.30 $\pm$23.41  & 0.03 $\pm$0.004\tabularnewline
\hline 
LR  & 82.1 $\pm$0.25 & 14.62 $\pm$7.92  & 24.79 $\pm$15.08  & 44.57 $\pm$24.27  & 56.85 $\pm$35.07  & 0.002 $\pm$0.0005\tabularnewline
\hline 
SVM  & 83.5 $\pm$0.21  & 14.01 $\pm$7.61  & 25.61 $\pm$15.30  & 40.66 $\pm$16.03  & 53.28 $\pm$18.45  & 0.02 $\pm$0.02\tabularnewline
\hline 
\end{tabular}
\label{Table:case2results}
\end{table}

\begin{table}
\caption{Predicting Total sales for PublishingHouse704 (highest number of different titles sold)}
\centering{}%
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
 &  $R^{2}$  & MAE  & RMSE  & RAE (\%)  & RRSE (\%)  & Time (s)\tabularnewline
\hline 
\hline 
M5P  & 88.9 $\pm$0.07 & 71.26 $\pm$21.29  & 125.19 $\pm$50.09  & 39.25 $\pm$11.77  & 47.50 $\pm$15.93  & 0.05 $\pm$0.03\tabularnewline
\hline 
K-NN  & 82.6 $\pm$0.10  & 87.60 $\pm$23.21  & 158.63 $\pm$54.16  & 47.62 $\pm$10.32  & 59.17 $\pm$14.43  & 0.0001 $\pm$0.0003\tabularnewline
\hline 
RF & 87.1 $\pm$0.08  & 74.63 $\pm$22.17  & 139.74 $\pm$54.36  & 40.62 $\pm$10.21  & 52.22 $\pm$16.27  & 0.11 $\pm$0.01\tabularnewline
\hline 
LR  & 83.8 $\pm$0.09  & 97.51 $\pm$18.87  & 155.27 $\pm$45.56  & 54.17 $\pm$13.60  & 60.31 $\pm$21.17  & 0.01 $\pm$0.001\tabularnewline
\hline 
SVM  & 87.4 $\pm$0.07  & 78.74 $\pm$22.25  & 147.30 $\pm$57.99  & 42.43 $\pm$7.83  & 53.29 $\pm$9.35  & 0.06 $\pm$0.016\tabularnewline
\hline 
\end{tabular}
\label{Table:case3results}
\end{table}

\begin{table}
\caption{Predicting Total sales for PublishingHouse-UDLU11 (medium number of different books sold))}
\centering{}%
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
 & $R^{2}$  & MAE  & RMSE  & RAE (\%)  & RRSE (\%)  & Time (s)\tabularnewline
\hline 
\hline 
M5P  & 77.5 $\pm$0.15  & 573.41 $\pm$192.22  & 860.31 $\pm$456.22  & 58.26 $\pm$15.87  & 66.00 $\pm$29.45  & 0.024 $\pm$0.002\tabularnewline
\hline 
K-NN  & 73.2 $\pm$0.16  & 596.62 $\pm$205.37  & 933.06 $\pm$356.11  & 60.62 $\pm$17.85  & 71.36 $\pm$22.34  & 0 $\pm$0.0002\tabularnewline
\hline 
RF & 86.7 $\pm$0.07  & 449.16 $\pm$127.80  & 671.76 $\pm$212.74  & 45.58 $\pm$9.80  & 51.37 $\pm$11.16  & 0.06 $\pm$0.01\tabularnewline
\hline 
LR  & 73.3 $\pm$0.20  & 680.16 $\pm$263.79  & 1103.97 $\pm$850.69  & 69.78 $\pm$27.24  & 86.11 $\pm$71.32  & 0.002 $\pm$0.001\tabularnewline
\hline 
SVM  & 80.4 $\pm$0.12  & 529.35 $\pm$172.50  & 846.01 $\pm$341.12  & 53.26 $\pm$11.92  & 63.54 $\pm$18.25  & 0.03 $\pm$0.02\tabularnewline
\hline 
\end{tabular}
\label{Table:case4results}
\end{table}

@@

\begin{table}[!ht]
\caption{Predicting Total sales for PublishingHouse-UDL929 (ReliefFAttributeEval-FS)}
\centering{}%
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
 & $R^{2}$  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\tabularnewline
\hline 
\hline 
M5P & 90.5 $\pm$0.1 & 661.81 $\pm$186.17 & 1070.24 $\pm$425.66 & 40.18 $\pm$10.50 & 43.56 $\pm$19.77 & 0.02 $\pm$0.002\tabularnewline
\hline 
K-NN & 87.8 $\pm$0.11 & 751.54 $\pm$270.91 & 1257.82 $\pm$615.66& 44.57 $\pm$10.89 & 48.62 $\pm$18.73 & 0.0001 $\pm$0.0003\tabularnewline
\hline 
RF & 88.3 $\pm$0.11 & 735.04 $\pm$326.9 & 1420.43 $\pm$941.62 & 43.56 $\pm$15.88 & 54.36 $\pm$35.31 & 0.10 $\pm$0.009\tabularnewline
\hline 
LR & 88.4 $\pm$0.11 & 868.18 $\pm$208.65 & 1231.23 $\pm$454.86 & 53.38 $\pm$14.67 & 50.60 $\pm$22.04 & 0.0006 $\pm$0.0005\tabularnewline
\hline 
SVM & 87.6 $\pm$0.10 & 860.49 $\pm$334.67 & 1560.05 $\pm$962.64 & 49.98 $\pm$9.68 & 55.07 $\pm$17.76 & 0.023 $\pm$0.003\tabularnewline
\hline 
\end{tabular}
\label{Table:case1results-RAE}
\end{table}

\begin{table}[!ht]
\caption{Predicting Total sales for PublishingHouse-UDLW12 (ReliefFAttributeEval-FS)}
\centering{}%
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
 & $R^{2}$  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\tabularnewline
\hline 
\hline 
M5P & 83.7 $\pm$0.24 & 13.85 $\pm$6.56 & 23.19 $\pm$11.80 & 42.35 $\pm$20.33 & 54.08 $\pm$30.06 & 0.0063 $\pm$0.0014\tabularnewline
\hline 
K-NN & 77.2 $\pm$0.30 & 14.18 $\pm$6.63 & 23.65 $\pm$11.03 & 43.37 $\pm$19.23 & 57.00 $\pm$30.59 & 0 $\pm$0.0001\tabularnewline
\hline 
RF & 86.7 $\pm$0.16 & 13.63 $\pm$6.67 & 22.80 $\pm$11.81 & 41.07 $\pm$17.71 & 52.43 $\pm$26.23 & 0.0304 $\pm$0.0025\tabularnewline
\hline 
LR & 84.4 $\pm$0.25 & 12.79 $\pm$6.65 & 21.52 $\pm$12.54 & 39.47 $\pm$23.35 & 50.14 $\pm$35.26 & 0.0005 $\pm$0.0005\tabularnewline
\hline 
SVM & 85.2 $\pm$0.19 & 13.22 $\pm$7.39 & 24.41 $\pm$15.09 & 38.24 $\pm$15.41 & 50.46 $\pm$17.97 & 0.014 $\pm$0.002\tabularnewline
\hline 
\end{tabular}
\label{Table:case2results-RAE}
\end{table}

\begin{table}[!ht]
\caption{Predicting Total sales for PublishingHouse704 (ReliefFAttributeEval-FS) }
\centering{}%
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
 & $R^{2}$  & MAE  & RMSE  & RAE (\%)  & RRSE (\%)  & Time (s)\tabularnewline
\hline 
\hline 
M5P  & 89.3 $\pm$0.08  & 69.70 $\pm$19.85  & 122.48 $\pm$47.28  & 38.49 $\pm$11.53  & 46.68 $\pm$16.02 & 0.028 $\pm$0.003\tabularnewline
\hline 
K-NN  & 85.6 $\pm$0.10  & 78.39 $\pm$24.12  & 147.07 $\pm$58.02  & 42.58 $\pm$10.99  & 54.42 $\pm$15.54  & 0.0001 $\pm$0.0003\tabularnewline
\hline 
RF & 87.7 $\pm$0.08  & 73.13 $\pm$22.95  & 137.60 $\pm$56.14  & 39.79 $\pm$10.69  & 51.35 $\pm$17.00  & 0.13 $\pm$0.01\tabularnewline
\hline 
LR  & 87.3 $\pm$0.06  & 89.72 $\pm$18.31  & 140.65 $\pm$47.12  & 49.45 $\pm$10.50  & 53.20 $\pm$14.16  & 0.0008 $\pm$0.0005\tabularnewline
\hline 
SVM  & 87.7 $\pm$0.07  & 77.30 $\pm$22.25  & 146.46 $\pm$57.68  & 41.67 $\pm$7.99  & 53.10 $\pm$9.51  & 0.05 $\pm$0.02\tabularnewline
\hline 
\end{tabular}
\label{Table:case3results-RAE}
\end{table}

\begin{table}[!ht]
\caption{Predicting Total sales for PublishingHouse-UDLU11 (ReliefFAttributeEval-FS)}
\centering{}%
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
 & $R^{2}$  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\tabularnewline
\hline 
\hline 
M5P & 76.6 $\pm$0.17 & 592.49 $\pm$209.25 & 894.76 $\pm$508.14 & 60.21 $\pm$18.22 & 69.14 $\pm$37.35 & 0.02$\pm$0.001\tabularnewline
\hline 
K-NN & 82.7 $\pm$0.09 & 487.00 $\pm$140.27 & 741.81 $\pm$238.56 & 49.27 $\pm$10.50 & 56.62 $\pm$12.59 & 0.0001 $\pm$0.0003\tabularnewline
\hline 
RF & 85.3 $\pm$0.09 & 455.7 $\pm$123.96 & 686.54 $\pm$198.16 & 46.32 $\pm$10.20 & 53.03 $\pm$13.05 & 0.07 $\pm$0.003\tabularnewline
\hline 
LR & 64.4 $\pm$0.20 & 817.21 $\pm$331.16 & 1324.05 $\pm$1090.85 & 83.22 $\pm$32.01 & 101.90 $\pm$87.83 & 0.0005 $\pm$0.0005\tabularnewline
\hline 
SVM & 71.4 $\pm$0.14 & 644.42 $\pm$203.43 & 1009.66 $\pm$371.83 & 64.47 $\pm$11.70 & 75.54 $\pm$15.99 & 0.018 $\pm$0.001\tabularnewline
\hline 
\end{tabular}
\label{Table:case4results-RAE}
\end{table}

@@

Figure \ref{fig:decision_tree_best_seller_fs} shows the decision tree obtained for the same publishing house (the same data, but just considering the selected features by ReliefAttributeEval method, since it is the one which yields the best results).

>>>>

With this issue in mind, in this paper we firstly present an analysis on the aforementioned real dataset, by means of data mining and visualisation techniques. Then, a feature selection process is conducted using three different methods, in order to find out what are the relevant variables describing a book in the prediction (or regression) procedure. After this, a forecasting stage is performed applying a set of regression algorithms to the different datasets (considering a different number of variables).
The value of this methodology is contrasted considering four different publishing companies being representative as top sellers, medium sellers, the most varied and one which sells a medium amount of different books.

The rest of this paper is structured as follows: next, Section \ref{sec:soa} presents a comprehensive review of the approaches found in the bibliography related to the prediction of sales in similar scopes. 
Then, Section \ref{sec:problem} introduces the problem of the estimation of print-run for new books, along with a description of the considered dataset.
Section \ref{sec:methodology} details the methodology considered in the study, from the data collection and preprocessing stages, to the selection of the forecasting methods to be applied in the experiments.  These are reported in Section \ref{sec:experiments}, which is also devoted to analyse the obtained results in feature selection and book sales forecasting using different datasets (with different amounts of features) for all the publishing companies. The results obtained for the four considered special cases are commented in Section \ref{sec:example_cases}. Finally, conclusions and future lines of work are presented in Section \ref{sec:conclusionsAndFutureWork}.

@@

First, after the publishing company has provided the raw data
(extracted directly from its database), a preprocessing method has
% This should go to the previous section. 
been performed in order to remove incorrect or incoherent patterns,
such as those with null values in required variables, or with negative
sales, for instance. Moreover, the initial set of variables (presented
in Table \ref{tabla:paramsOrig50}) has been reduced by an expert to
use just those that can be known in advance when a new book is
launched, i.e. \textit{pre-sales data}.

@@

Once the models and results have been obtained for the whole dataset, the same methodology has been applied to some specific cases (publishing companies) in order to prove the value of the proposal.
Some specific interpretable models have been created as a final result of the work. The aim is that these will cold be used as a decision-aid tool for the experts who have to take decide about the best print-run quantity for new published books, in order to, logically maximise the benefit (or minimise the costs).

@@

Regarding the feature \textit{publisher}, we have removed it from the final dataset since it is indeed included in the code of \texttt{collection}. In addition, we think it is not really relevant for the accuracy of the models and, moreover, publishers will not consider the results in other publishing companies for predicting its own sales.
% Antonio - Think about this... should we mention this?

@@

We have analysed the whole dataset (all the publishing companies), but also performed some experiments considering specific publishing companies as example cases.
The obtained decision trees have been plotted to show their simplicity and their real value as a decision-aid tool for publishers.

@@

\section{Experiments of special publishing companies cases}
\label{sec:example_cases}

This section presents further experiments conducted on data concerning four interesting special publishing company cases. These publishing companies were selected as representative cases which could be very interesting for decision makers and managers in the domain. The four cases are described as follows:

\begin{itemize}
    \item Best seller publishing company: this case represents the publishing company that sells the highest number of copies regardless the title of the books sold. Therefore, it is an example of a case on a higher business scale.
    \item Medium seller publishing company: this represents an publishing company that sells medium number of copies compared to the other publishing companies (Medium business scale). 
    \item Highest variation publishing company: this is an example of an publishing company that follows a strategy in publishing a very wide range of different titles.
    \item Medium varied publishing company: this case represents an publishing company that has a median rank between the other publishing company regarding the variety of titles sold.
\end{itemize}

Table \ref{Table:special_cases} shows number of sold copies and number of titles published by the selected publishing companies.

\begin{table}
\caption{Description of publishing companies considered as special cases.
\label{tab:desc_publishing companies}}
\centering{}%
\begin{tabular}{|c|l|l|l|}
\hline 
 Case & Different books sold & Total copies sold & Description\\
\hline 
\textit{All publishing companies} & 6083 & 3201645 & 209 publishing companies\\
\hline 
\textit{UDL929} & 216 & 460752 & Best selling publishing company\\
\hline 
\textit{UDLW12} & 97 & 2635 & Medium selling publishing company\\
\hline 
\textit{UDL704} & 293 & 58236 & publishing company with most different\\ 
       &     &       & books sold\\
\hline 
\textit{UDLU11} & 180 & 249481 & publishing company with medium number\\ 
       &     &       &  of different books sold\\
\hline 
\end{tabular}
\label{Table:special_cases}
\end{table}

@@

\begin{table}
\caption{Predicting Total sales for publishing company-UDL929 (The best selling publishing company) }
\centering{}%
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
 & $R^{2}$  & MAE  & RMSE  & RAE (\%)  & RRSE (\%)  & Time (s)\tabularnewline
\hline 
\hline 
M5P  & 90.0 $\pm$0.10 & 670.24 $\pm$181.05  & 1065.34 $\pm$413.84  & 40.83 $\pm$10.86  & 43.56 $\pm$19.87  & 0.03 $\pm$0.002\tabularnewline
\hline 
K-NN  & 73.3 $\pm$0.19  & 1057.21 $\pm$385.04  & 1875.85 $\pm$916.96  & 61.88 $\pm$12.37  & 68.75 $\pm$15.98  & 0 $\pm$0.0001\tabularnewline
\hline 
RF  & 87.6 $\pm$0.11  & 771.83 $\pm$326.34  & 1490.49 $\pm$930.58  & 45.40 $\pm$14.14  & 55.91 $\pm$31.70  & 0.08 $\pm$0.004\tabularnewline
\hline 
LR  & 86.3 $\pm$0.12  & 922.33 $\pm$289.01  & 1399.84 $\pm$619.62  & 56.11 $\pm$16.17  & 56.43 $\pm$25.09  & 0.005 $\pm$0.001\tabularnewline
\hline 
SVM  & 86.7 $\pm$0.1  & 873.22 $\pm$345.16 & 1621.48 $\pm$985.24  & 50.85 $\pm$11.83  & 57.23 $\pm$20.40  & 0.04 $\pm$0.016\tabularnewline
\hline 
\end{tabular}
\label{Table:case1results}
\end{table}

\begin{table}
\caption{Predicting Total sales for PublishingCo-UDLW12 (The median selling publishing company) }
\centering{}%
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
 & $R^{2}$  & MAE  & RMSE  & RAE (\%)  & RRSE (\%)  & Time (s)\tabularnewline
\hline 
\hline 
M5P  & 83.2 $\pm$0.24  & 14.18 $\pm$6.62  & 23.82 $\pm$11.86  & 43.41 $\pm$20.39  & 55.79 $\pm$30.47  & 0.009 $\pm$0.002\tabularnewline
\hline 
K-NN  & 79.3 $\pm$0.24 & 15.34 $\pm$8.71  & 26.57 $\pm$16.64  & 46.20 $\pm$23.77  & 60.09 $\pm$35.21  & 0.0001 $\pm$0.0002\tabularnewline
\hline 
RF & 85.8 $\pm$0.17  & 14.19 $\pm$6.69  & 23.57 $\pm$11.83  & 42.53 $\pm$16.80  & 53.30 $\pm$23.41  & 0.03 $\pm$0.004\tabularnewline
\hline 
LR  & 82.1 $\pm$0.25 & 14.62 $\pm$7.92  & 24.79 $\pm$15.08  & 44.57 $\pm$24.27  & 56.85 $\pm$35.07  & 0.002 $\pm$0.0005\tabularnewline
\hline 
SVM  & 83.5 $\pm$0.21  & 14.01 $\pm$7.61  & 25.61 $\pm$15.30  & 40.66 $\pm$16.03  & 53.28 $\pm$18.45  & 0.02 $\pm$0.02\tabularnewline
\hline 
\end{tabular}
\label{Table:case2results}
\end{table}

\begin{table}
\caption{Predicting Total sales for PublishingCo704 (highest number of different titles sold)}
\centering{}%
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
 &  $R^{2}$  & MAE  & RMSE  & RAE (\%)  & RRSE (\%)  & Time (s)\tabularnewline
\hline 
\hline 
M5P  & 88.9 $\pm$0.07 & 71.26 $\pm$21.29  & 125.19 $\pm$50.09  & 39.25 $\pm$11.77  & 47.50 $\pm$15.93  & 0.05 $\pm$0.03\tabularnewline
\hline 
K-NN  & 82.6 $\pm$0.10  & 87.60 $\pm$23.21  & 158.63 $\pm$54.16  & 47.62 $\pm$10.32  & 59.17 $\pm$14.43  & 0.0001 $\pm$0.0003\tabularnewline
\hline 
RF & 87.1 $\pm$0.08  & 74.63 $\pm$22.17  & 139.74 $\pm$54.36  & 40.62 $\pm$10.21  & 52.22 $\pm$16.27  & 0.11 $\pm$0.01\tabularnewline
\hline 
LR  & 83.8 $\pm$0.09  & 97.51 $\pm$18.87  & 155.27 $\pm$45.56  & 54.17 $\pm$13.60  & 60.31 $\pm$21.17  & 0.01 $\pm$0.001\tabularnewline
\hline 
SVM  & 87.4 $\pm$0.07  & 78.74 $\pm$22.25  & 147.30 $\pm$57.99  & 42.43 $\pm$7.83  & 53.29 $\pm$9.35  & 0.06 $\pm$0.016\tabularnewline
\hline 
\end{tabular}
\label{Table:case3results}
\end{table}

\begin{table}
\caption{Predicting Total sales for PublishingCo-UDLU11 (medium number of different books sold))}
\centering{}%
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
 & $R^{2}$  & MAE  & RMSE  & RAE (\%)  & RRSE (\%)  & Time (s)\tabularnewline
\hline 
\hline 
M5P  & 77.5 $\pm$0.15  & 573.41 $\pm$192.22  & 860.31 $\pm$456.22  & 58.26 $\pm$15.87  & 66.00 $\pm$29.45  & 0.024 $\pm$0.002\tabularnewline
\hline 
K-NN  & 73.2 $\pm$0.16  & 596.62 $\pm$205.37  & 933.06 $\pm$356.11  & 60.62 $\pm$17.85  & 71.36 $\pm$22.34  & 0 $\pm$0.0002\tabularnewline
\hline 
RF & 86.7 $\pm$0.07  & 449.16 $\pm$127.80  & 671.76 $\pm$212.74  & 45.58 $\pm$9.80  & 51.37 $\pm$11.16  & 0.06 $\pm$0.01\tabularnewline
\hline 
LR  & 73.3 $\pm$0.20  & 680.16 $\pm$263.79  & 1103.97 $\pm$850.69  & 69.78 $\pm$27.24  & 86.11 $\pm$71.32  & 0.002 $\pm$0.001\tabularnewline
\hline 
SVM  & 80.4 $\pm$0.12  & 529.35 $\pm$172.50  & 846.01 $\pm$341.12  & 53.26 $\pm$11.92  & 63.54 $\pm$18.25  & 0.03 $\pm$0.02\tabularnewline
\hline 
\end{tabular}
\label{Table:case4results}
\end{table}

@@

\begin{table}[!ht]
\caption{Predicting Total sales for PublishingCo-UDL929 (ReliefFAttributeEval-FS)}
\centering{}%
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
 & $R^{2}$  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\tabularnewline
\hline 
\hline 
M5P & 90.5 $\pm$0.1 & 661.81 $\pm$186.17 & 1070.24 $\pm$425.66 & 40.18 $\pm$10.50 & 43.56 $\pm$19.77 & 0.02 $\pm$0.002\tabularnewline
\hline 
K-NN & 87.8 $\pm$0.11 & 751.54 $\pm$270.91 & 1257.82 $\pm$615.66& 44.57 $\pm$10.89 & 48.62 $\pm$18.73 & 0.0001 $\pm$0.0003\tabularnewline
\hline 
RF & 88.3 $\pm$0.11 & 735.04 $\pm$326.9 & 1420.43 $\pm$941.62 & 43.56 $\pm$15.88 & 54.36 $\pm$35.31 & 0.10 $\pm$0.009\tabularnewline
\hline 
LR & 88.4 $\pm$0.11 & 868.18 $\pm$208.65 & 1231.23 $\pm$454.86 & 53.38 $\pm$14.67 & 50.60 $\pm$22.04 & 0.0006 $\pm$0.0005\tabularnewline
\hline 
SVM & 87.6 $\pm$0.10 & 860.49 $\pm$334.67 & 1560.05 $\pm$962.64 & 49.98 $\pm$9.68 & 55.07 $\pm$17.76 & 0.023 $\pm$0.003\tabularnewline
\hline 
\end{tabular}
\label{Table:case1results-RAE}
\end{table}

\begin{table}[!ht]
\caption{Predicting Total sales for PublishingCo-UDLW12 (ReliefFAttributeEval-FS)}
\centering{}%
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
 & $R^{2}$  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\tabularnewline
\hline 
\hline 
M5P & 83.7 $\pm$0.24 & 13.85 $\pm$6.56 & 23.19 $\pm$11.80 & 42.35 $\pm$20.33 & 54.08 $\pm$30.06 & 0.0063 $\pm$0.0014\tabularnewline
\hline 
K-NN & 77.2 $\pm$0.30 & 14.18 $\pm$6.63 & 23.65 $\pm$11.03 & 43.37 $\pm$19.23 & 57.00 $\pm$30.59 & 0 $\pm$0.0001\tabularnewline
\hline 
RF & 86.7 $\pm$0.16 & 13.63 $\pm$6.67 & 22.80 $\pm$11.81 & 41.07 $\pm$17.71 & 52.43 $\pm$26.23 & 0.0304 $\pm$0.0025\tabularnewline
\hline 
LR & 84.4 $\pm$0.25 & 12.79 $\pm$6.65 & 21.52 $\pm$12.54 & 39.47 $\pm$23.35 & 50.14 $\pm$35.26 & 0.0005 $\pm$0.0005\tabularnewline
\hline 
SVM & 85.2 $\pm$0.19 & 13.22 $\pm$7.39 & 24.41 $\pm$15.09 & 38.24 $\pm$15.41 & 50.46 $\pm$17.97 & 0.014 $\pm$0.002\tabularnewline
\hline 
\end{tabular}
\label{Table:case2results-RAE}
\end{table}

\begin{table}[!ht]
\caption{Predicting Total sales for PublishingCo704 (ReliefFAttributeEval-FS) }
\centering{}%
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
 & $R^{2}$  & MAE  & RMSE  & RAE (\%)  & RRSE (\%)  & Time (s)\tabularnewline
\hline 
\hline 
M5P  & 89.3 $\pm$0.08  & 69.70 $\pm$19.85  & 122.48 $\pm$47.28  & 38.49 $\pm$11.53  & 46.68 $\pm$16.02 & 0.028 $\pm$0.003\tabularnewline
\hline 
K-NN  & 85.6 $\pm$0.10  & 78.39 $\pm$24.12  & 147.07 $\pm$58.02  & 42.58 $\pm$10.99  & 54.42 $\pm$15.54  & 0.0001 $\pm$0.0003\tabularnewline
\hline 
RF & 87.7 $\pm$0.08  & 73.13 $\pm$22.95  & 137.60 $\pm$56.14  & 39.79 $\pm$10.69  & 51.35 $\pm$17.00  & 0.13 $\pm$0.01\tabularnewline
\hline 
LR  & 87.3 $\pm$0.06  & 89.72 $\pm$18.31  & 140.65 $\pm$47.12  & 49.45 $\pm$10.50  & 53.20 $\pm$14.16  & 0.0008 $\pm$0.0005\tabularnewline
\hline 
SVM  & 87.7 $\pm$0.07  & 77.30 $\pm$22.25  & 146.46 $\pm$57.68  & 41.67 $\pm$7.99  & 53.10 $\pm$9.51  & 0.05 $\pm$0.02\tabularnewline
\hline 
\end{tabular}
\label{Table:case3results-RAE}
\end{table}

\begin{table}[!ht]
\caption{Predicting Total sales for PublishingCo-UDLU11 (ReliefFAttributeEval-FS)}
\centering{}%
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
 & $R^{2}$  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\tabularnewline
\hline 
\hline 
M5P & 76.6 $\pm$0.17 & 592.49 $\pm$209.25 & 894.76 $\pm$508.14 & 60.21 $\pm$18.22 & 69.14 $\pm$37.35 & 0.02$\pm$0.001\tabularnewline
\hline 
K-NN & 82.7 $\pm$0.09 & 487.00 $\pm$140.27 & 741.81 $\pm$238.56 & 49.27 $\pm$10.50 & 56.62 $\pm$12.59 & 0.0001 $\pm$0.0003\tabularnewline
\hline 
RF & 85.3 $\pm$0.09 & 455.7 $\pm$123.96 & 686.54 $\pm$198.16 & 46.32 $\pm$10.20 & 53.03 $\pm$13.05 & 0.07 $\pm$0.003\tabularnewline
\hline 
LR & 64.4 $\pm$0.20 & 817.21 $\pm$331.16 & 1324.05 $\pm$1090.85 & 83.22 $\pm$32.01 & 101.90 $\pm$87.83 & 0.0005 $\pm$0.0005\tabularnewline
\hline 
SVM & 71.4 $\pm$0.14 & 644.42 $\pm$203.43 & 1009.66 $\pm$371.83 & 64.47 $\pm$11.70 & 75.54 $\pm$15.99 & 0.018 $\pm$0.001\tabularnewline
\hline 
\end{tabular}
\label{Table:case4results-RAE}
\end{table}

@@

Figure \ref{fig:decision_tree_best_seller_fs} shows the decision tree obtained for the same publishing company (the same data, but just considering the selected features by ReliefAttributeEval method, since it is the one which yields the best results).
